A Switching Planner for Combined Task and Observation Planning

### 2010-11-24 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/prop-dtp.tex
Edits to early sections

\noindent Finally, it is
useful to note that there is a corresponding deterministic FSCs for
both sequential (e.g., conformant) and contingent plans.

>>>>

\noindent Finally, it is
useful to note that there is a corresponding deterministic FSCs for
both sequential (e.g., conformant) and contingent plan formats.
